Red-Giant Hot Jupiters: Brilliant Radio Beacons?

### 2015-05-18 ms.tex
estimate for radio brightness of RGs is updated

In the radio range, the brightness source of the radio emission is Rayleigh-Jeans tail of the Planck function, i.e., $S_{\nu } = 2kT\nu^2/c^2$. Recent observations revealed that this dependence on $\nu$ ($f \propto \nu^{\alpha }$ where $\alpha $ is 2) can approximately be extended as low frequency as 1 GHz \citep{gorman2013}, presumably as a result of the wavelength dependence of the opacity (at longer wavelength we see the region further from the center of the stars) and the decreased temperature as the distance from the stars increases. 
In this paper, we simply assume that the radio emission from the red giants themselves is approximated as a black body radiation at 1000~GHz and proportional to $\nu ^2$. 
Thus, the flux from the giants is:
%%%
\begin{eqnarray}
f_{\star } (\nu ) &=& \frac{2R_{\star }^2 k_B T \nu^2}{c^2 d^2}  \\
&\approx & 1.4 \times 10^{-5} ~\mbox{Jy} \left( \frac{d}{10 ~\mbox{pc}} \right)^{-2} \\
&& \times \left( \frac{R_{\star }}{10 R_{\odot }} \right)^2 \left( \frac{T_{\star }}{10^{4}~\mbox{K}} \right) \left( \frac{\nu}{1 ~\mbox{GHz}} \right)^2 
\end{eqnarray}
%%%
The brightest emission due to interaction with planetary companion would overwhelm radio emission from their host (evolved) star in the 10-100~MHz range (in the 100-1000~MHz range) if the stellar radius $R_{\star }$ is smaller than $\sim 1000R_{\odot }$ ($\sim 100R_{\odot }$).

>>>>

In the radio range, the brightness source of the radio emission is Rayleigh-Jeans tail of the Planck function, i.e., $S_{\nu } = 2kT\nu^2/c^2$. Recent observations revealed that this dependence on $\nu$ ($f \propto \nu^{\alpha }$ where $\alpha $ is 2) can approximately be extended as low frequency as 1 GHz \citep{gorman2013}, presumably as a result of the wavelength dependence of the opacity (at longer wavelength we see the region further from the center of the stars) and the decreased temperature as the distance from the stars increases. 
In this paper, we simply assume that the radio emission from the red giants themselves is approximated as a black body radiation at 1000~GHz and proportional to $\nu ^{5/3}$. 
Thus, the flux from the giants is:
%%%
\begin{eqnarray}
f_{\star } (\nu ) &=& \frac{2R_{\star }^2 k_B T \nu^2}{c^2 d^2}  \\
&\approx & 1.56 \times 10^{-6} ~\mbox{Jy} \left( \frac{d}{10 ~\mbox{pc}} \right)^{-2} \\
&& \times \left( \frac{R_{\star }}{10 R_{\odot }} \right)^2 \left( \frac{T_{\star }}{10^{4}~\mbox{K}} \right) \left( \frac{\nu}{1~\mbox{GHz}} \right)^{5/3} 
\end{eqnarray}
%%%
The brightest emission due to interaction with planetary companion to the RGB stars would therefore overwhelm the radio emission from their host stars in the 10-100~MHz range (in the 100-1000~MHz range) unless the stellar radius $R_{\star }$ is larger than $\sim 2000R_{\odot }$ ($\sim 300R_{\odot }$).
